Identification of protoneutron star g-modes in gravitational-wave data

### 2020-08-12 results.tex
changes

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/s20-gw_covpbb_prec_aLIGO}
 \caption{$covpbb$ and $precision$ for {\tt s20-gw-10kpc} signal embedded in aLIGO noise at different distance from the Earth. The shaded regions are given by the median absolute deviation.} \label{fig:s20results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/covppb_all_aLIGO}
 \caption{$covpbb$ for 7 waveforms embedded in aLIGO noise at different distance from the Earth. } \label{fig:aLIGOall}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/s20-gw_covpbb_prec_aLIGO}
 \caption{$coverage$ and $precision$ for {\tt s20-gw-10kpc} signal embedded in aLIGO noise at different distance from the Earth. The shaded regions are given by the median absolute deviation.} \label{fig:s20results}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/covppb_all_aLIGO}
 \caption{$coverage$ for 7 waveforms embedded in aLIGO noise at different distance from the Earth. } \label{fig:aLIGOall}
\end{figure}
